Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-06-10 doc/thesis/discussion.Rnw
Some results

@@

@@

{\color{blue}\uline{
The estimates of the prevalence \gls{I} were largely robust to the choice of
prior on \gls{m}} (\cref{fig:abchpd,fig:abchpdm2}).
\textcite{niculescu2015recent} \uline{reported that 494 new HIV infections were
diagnosed among the studied population (\glspl{IDU} in Bucharest) during the
study period. Our estimate of the prevalence was higher (X), although the 95\%
\gls{HPD} interval did contain the value 494. In addition, it is not
unreasonable that a substantial fraction of the \gls{HIV}-positive individuals
in an \gls{IDU} population could be undiagnosed, given that these populations
are often marginalized.}

@@

\textcite{cuevas2009hiv} \uline{reported that 620 newly infected and 1500
chronically infected patients had been sampled during the study period, for a
total of 2120. This is substantially greater than the point estimate of X we
obtained with \gls{ABC}, even without considering the likely possibility that
there were more infected than sampled individuals. Again, this error may in
part be due to model misspecification, which highlights the importance of
selecting a model appropriate to the dataset at hand.} }

>>>>

\subsubsection{Preferential attachment power}

@@

\subsubsection{Power law exponent}

@@

\subsubsection{HIV prevalence}

{\color{blue}\uline{The true \gls{HIV} prevalence in a population can be
difficult to estimate for several reasons. \gls{HIV}-infected individuals may
be asymptomatic for months or years, possibly delaying their awareness of their
status. In many contexts, the risk factors for acquisition of \gls{HIV} are
illegal or stigmatized, which may represent a barrier to testing, treatment,
and/or disclosure of status. Several of the studies whose data we analysed
report the number of new infections over the study period. We expect these
numbers to be lower, perhaps substantially, than the true prevalence. We also
note that our simulation study showed that the estimates of \gls{I} obtained
with \software{netabc} were upwardly biased, the severity increasing with the
true value of \gls{I}. In addition, our initial exploratory analysis showed
that the identifiability of \gls{I} decreases with the number of sampled tips 
(\cref{fig:Icrossv,fig:Ikpca}). In real world studies, the proportion of
infected individuals sampled is usually low, whic may imede our ability to
estimate \gls{I}.

The estimates of the prevalence \gls{I} were largely robust to the choice of
prior on \gls{m}} (\cref{fig:abchpd,fig:abchpdm2}).

\textcite{niculescu2015recent} and \textcite{zetterberg2004two} both reported 
on epidemics in \gls{IDU} populations in Eastern Europe (Romania and Estonia,
respectively). The point estimates of \gls{I} for these two datasets were
similar (X and X), although the confidence interval around the
\textcite{niculescu2015recent} data was wider. \textcite{niculescu2015recent}
\uline{reported that 494 new \gls{HIV} infections were diagnosed among the
studied population (\glspl{IDU} in Bucharest) during the study period, and this
value was contained in our 95\% \gls{HPD} (X-X). On the other hand,
\textcite{zetterberg2004two} collected samples from several locations
throughout Estonia; using their reported incidence estimates, there were
approximately 2000 new infections in the country during the study period. This
value was outside our 95\% \gls{HPD} (X-X). The authors indicated that their
sample was ``convenience based''. It is possible that other, harder-to-reach
individuals had no contacts with those sampled, which would reduce the apparent
network size. Alternatively, the low estimated prevalence may have been due to
the low sampling fraction.}

\uline{The cluster we analysed within the BC data consists primarily of
\gls{IDU} in Vancouver's downtown east side. This population has been
intensively targeted by public health interventions. Combined with the routine 
clinical genotyping performed in BC for all new \gls{HIV} infections, it is not
unreasonable to suppose that the sampled individuals (399) comprise the
majority of \gls{HIV}-positive network members.

\textcite{wang2015targeting} and \textcite{li2015hiv} studied \gls{MSM}
populations in major Chinese cities (Shanghai and Beijing).

@@

\textcite{cuevas2009hiv} \uline{reported that 620 newly infected and 1500
chronically infected patients had been sampled during the study period, for a
total of 2120. This is substantially greater than the point estimate of X we
obtained with \gls{ABC}, even without considering the likely possibility that
there were more infected than sampled individuals. Again, this error may in
part be due to model misspecification, which highlights the importance of
selecting a model appropriate to the dataset at hand.}}

\subsubsection{Caveats? TODO}
